---
title: "ETF Data Analysis"
format: 
  html:
    code-fold: true
    code-summary: "Show Code"
vignette: >
  %\VignetteIndexEntry{ETF Data Analysis}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: setup
#| include: false
#| error: true

# Robust Setup for CI
data_loaded <- FALSE
universe <- NULL
metadata <- NULL
history <- NULL

tryCatch({
  suppressPackageStartupMessages({
    library(etfdata)
    if (requireNamespace("ggplot2", quietly = TRUE)) library(ggplot2)
    if (requireNamespace("dplyr", quietly = TRUE)) library(dplyr)
    if (requireNamespace("targets", quietly = TRUE)) library(targets)
  })

  # Strategy: Load snapshot from installed package (CI) or source (Local)
  snapshot_file <- "vignette_data.rds"
  data_path <- system.file("extdata", snapshot_file, package = "etfdata")
  
  if (data_path == "" || !file.exists(data_path)) {
    # Try relative source path (Local dev)
    data_path <- file.path("..", "inst", "extdata", snapshot_file)
  }

  if (file.exists(data_path)) {
    snap <- readRDS(data_path)
    universe <- snap$universe
    metadata <- snap$metadata
    history <- snap$history
    data_loaded <- TRUE
  } else {
    # Fallback to targets if local
    if (dir.exists("../_targets")) {
      tar_config_set(store = "../_targets")
      universe <- tar_read(universe)
      metadata <- tar_read(metadata)
      history <- tar_read(history)
      data_loaded <- TRUE
    }
  }
}, error = function(e) {
  message("Setup failed: ", e$message)
})
```

## ETF Universe

We start by defining the universe of European UCITS ETFs. 

**Note:** The data displayed in this vignette is a subset (Top 5 by AUM) generated during the build process to ensure reproducibility and performance.

```{r universe-code}
#| echo: true
#| eval: false
# The function used to generate the full universe:
get_etf_universe
```

```{r universe-table}
#| echo: false
if (data_loaded && !is.null(universe)) {
  knitr::kable(head(universe))
} else {
  print("Universe data not available in this build.")
}
```

## Metadata (JustETF)

We scraped JustETF for metadata including AUM and TER.

```{r metadata-code}
#| echo: true
#| eval: false
# Code used:
fetch_etf_metadata(universe$isin)
```

```{r metadata-table}
#| echo: false
if (data_loaded && !is.null(metadata)) {
  # Check if columns exist before selecting
  cols <- c("isin", "aum_text", "ter_text", "replication")
  cols <- intersect(cols, colnames(metadata))
  if (length(cols) > 0) {
    knitr::kable(head(metadata[, cols, drop=FALSE]))
  }
} else {
  print("Metadata not available.")
}
```

## Price History (Yahoo Finance)

We fetched daily price history.

```{r history-plot}
#| echo: true
#| message: false
if (data_loaded && !is.null(history) && requireNamespace("ggplot2", quietly = TRUE)) {
  # Visualize Close Prices with Facets
  history %>%
    ggplot(aes(x = date, y = close, color = ticker)) +
    geom_line() +
    facet_wrap(~ticker, scales = "free_y") +
    labs(title = "ETF Price History (LSE)", y = "Close Price (GBP)") +
    theme_minimal() +
    theme(legend.position = "none")
} else {
  print("History plot not available.")
}
```

## Combined Analysis

Relationship between AUM and Liquidity (Volume)?

```{r combined}
#| echo: true
if (data_loaded && !is.null(history) && !is.null(metadata)) {
  # Join data
  avg_vol <- history %>%
    group_by(ticker) %>%
    summarise(avg_daily_vol = mean(volume, na.rm = TRUE))
  
  if ("isin" %in% colnames(universe) && "isin" %in% colnames(metadata)) {
    combined <- universe %>%
      inner_join(metadata, by = "isin") %>%
      inner_join(avg_vol, by = "ticker")
    
    # Parse AUM
    if (requireNamespace("stringr", quietly = TRUE) && requireNamespace("dplyr", quietly = TRUE)) {
       combined <- bind_cols(combined, parse_aum(combined$aum_text))
    }

    knitr::kable(head(combined %>% select(ticker, name, currency, aum_amount, aum_units, avg_daily_vol)))
  }
}
```

## Metadata

```{r session-info}
sessionInfo()
```

### Data Sizes

```{r data-sizes}
if (data_loaded) {
  print("Universe:")
  str(universe)
  print("Metadata:")
  str(metadata)
  print("History:")
  str(history)
}
```